What Happened to The Birth Rate?

### 2022-02-28 outputs/paper/paper.Rmd
Add lawmaking factors to LGBT analysis

@@

The percentage of LGBT (and many other gender identities) population has risen in recent years in the US, probably related to propaganda and political correctness.

Since there is not much data for other genders, and LGBT are the majorities, we will focus on LGBT population and the potential effect they bring to birth rate.

@@

We reproduced the plot showing Fertility Rate vs Mother's age from [@cite_original] in Figure \@ref(fig:cohort-plot). This plot is basically showing the fertility rate of women in different ages across 6 generations.
It's quite obvious that the 3 oldest cohorts (generations) have similar and higher fertility rates comparing to that of the 3 younger cohorts (generations).The 3 younger cohorts also have lower and lower fertility rate as their birthday moves forward (younger generation $\Rightarrow$ lower fertility rate).

Figure \@ref(fig:fig-parity) is a replication of a plot showing trends in births by "parity" (referring to the number of children for a given woman) from [@cite_original]. First and second births declined a lot since 2007, but the trend lines for third and higher order births are comparatively flat.
The women giving their 3rd and 4th births are most likely an older cohort than the cohorts giving their 1st and 2nd births. Again, this is another evidence showing the impact brought by cohort effects.

```{r echo = FALSE, fig-lgbt-trend-by-year, fig.cap='Socioeconomic Indicators', fig.asp=1, fig.ncol = 1, out.width='.80\\linewidth', fig.align="center"}
knitr::include_graphics("./images/US-LGBT-percent-trend.png")
```

```{r echo = FALSE, fig-lgbt-by-generation, fig.cap='Socioeconomic Indicators', fig.asp=1, fig.ncol = 1, out.width='.80\\linewidth', fig.align="center"}
knitr::include_graphics("./images/LGBT-percentage-by-generation.png")
```

>>>>

We reproduced the plot showing Fertility Rate vs Mother's age from [@cite_original] in Figure \@ref(fig:cohort-plot). This plot is basically showing the fertility rate of women in different ages across 6 generations.
It's quite obvious that the 3 oldest cohorts (generations) have similar and higher fertility rates comparing to that of the 3 younger cohorts (generations).The 3 younger cohorts also have lower and lower fertility rate as their birthday moves forward (younger generation $\Rightarrow$ lower fertility rate).
This reflects the impact to birth rate brought by cohort effects.

Figure \@ref(fig:fig-parity) is a replication of a plot showing trends in births by "parity" (referring to the number of children for a given woman) from [@cite_original]. First and second births declined a lot since 2007, but the trend lines for the third and higher order births are comparatively flat.
The women giving their 3rd and 4th births are most likely older cohorts comparing to the cohorts giving their 1st and 2nd births. Again, this is another evidence showing the impact brought by cohort effects.

"The explanation of cohort effects lies more in the way these cohorts were raised or in how they experienced their childhoods [@cite_original], than about a particular policy or cost factor post-2007"[@cite_original]. [@cite_original] claims that "this type of investigation is much harder to under-take with standard data and econometric techniques" and provided a some speculations, such as parents' expectation, resources (e.g. time and money) spent on children, etc.

We would like to raise another hypothesis related to effects to children from the society, laws and social medias, that's LGBT movement.

@@

The percentage of LGBT (and many other gender identities) population has risen in recent years in the US \@ref(fig:fig-lgbt-trend-by-year), probably related to propaganda in social medias, lawmaking and political correctness.
This research doesn't try to investigate the causes of LGBT population growth, and since there is not much data for other genders, and LGBT are the majorities, we will focus on LGBT population and the potential effect they brought to birth rate.

"On February 12, 2004, the first same-sex marriage in the United States happened in San Francisco, California."
"On May 17, 2004, Massachusetts became the first state and sixth jurisdiction in the world to legalize same-sex marriage."
"In 2008, California and Connecticut both legalized same-sex marriage, followed by Iowa, Vermont, and New Hampshire. Up until 2012, legalization came through state courts, the enactment of state legislation, or the result of the decisions of federal courts. On November 6, 2012, Maine, Maryland and Washington became the first states to legalize same-sex marriage through popular vote."
"On June 26, 2015, in the landmark civil rights case Obergefell v. Hodges, the Supreme Court ruled that the fundamental right to marry is guaranteed to same-sex couples by both the Due Process Clause and the Equal Protection Clause of the Fourteenth Amendment to the United States Constitution."[@same_sex_marriage_states_2022]
The first two dates mentioned above represents the beginning of the legalization of same-sex marriage in the US, and is quite close to 2007, when the significant drop of birth rate began. There may be a composition of effects causing the significant drop of birth rate in 2007, and the legalization of same-sex population could potentially be one of main causes.

@@

```{r echo = FALSE, fig-lgbt-trend-by-year, fig.cap='LGBT Population Percentage By Year', fig.asp=1, fig.ncol = 1, out.width='.80\\linewidth', fig.align="center"}
knitr::include_graphics("./images/US-LGBT-percent-trend.png")
```

```{r echo = FALSE, fig-lgbt-by-generation, fig.cap='LGBT Population Percentage By Generation', fig.asp=1, fig.ncol = 1, out.width='.80\\linewidth', fig.align="center"}
knitr::include_graphics("./images/LGBT-percentage-by-generation.png")
```
